Solutions to Integer Programming from Quantum Annealing

### 2020-09-04 paper/main.tex
Placing methods in the end
Major section refactor

Integer linear programming (ILP) is an integer optimization problem subject to inequality constraints and is a commonly tackled problem applicable to situations such as x~\cite{}, y~\cite{}, and the Minimum Dominating Set Problem (MDS)~\cite{}.
In general, however, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{}.
Standard classical heuristic algorithms employ a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem can be obtained in polynomial time, the optimal integer solution in general must be found in the $2^n$ integer solutions which surround the real number solution.
While greedy algorithms do not guarantee optimal global solutions, they find approximate solutions in polynomial time, which can be utilized in further computations.
Due to the importance and difficulty, in this work, we present a method to obtain the optimal solution to ILP by employing methods of quantum annealing.

@@

@@

@@

In section \ref{sec:methods} we propose an algorithm that maps ILP problems to QA hardware (\ref{sec:methods:ilp}) and present an example implementation in case of the Minimal Dominating Set problem (\ref{sec:methods:mds}).
We review the annealing process on the utilized hardware (\ref{sec:methods:annealing}) and describe the computational framework which we used to simulate the annealing process (\ref{sec:methods:simulation}).
Section \ref{sec:results} summarizes our findings and presents...
We conclude this report in \ref{sec:conclusion}.
All algorithms used and data obtained are publicly available (\ref{sec:open-source})

@@

%----------------------------------------------------------------------------------------
\subsection{Integer Programming Mapping to QUBO}
\label{sec:methods:ilp}
%----------------------------------------------------------------------------------------

This section presents the formalism which maps a general ILP to a QUBO.

%----------------------------------------------------------------------------------------
\subsubsection{Integer linear programming}
\label{sec:methods:ilp-def}
%----------------------------------------------------------------------------------------
Formally, ILP is defined as the optimization of a linear function
\begin{align}
 \label{eq:initial-ip-def}
 \vec x_0 = \mathrm{arg} & \min\limits_{x}(\sum_i c_i x_i)
\end{align}
subject to
\begin{align}
 \label{eq:ilp-constraints}
  & \sum_i A_{ai}x_i +b_a \leq 0 \,, \\
  & x_i  \in \mathbbm{N}
\end{align}

where the natural numbers $\mathbbm{N}$ include zero, $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.

%----------------------------------------------------------------------------------------
\subsubsection{Slack variables}
\label{sec:methods:slack}
%----------------------------------------------------------------------------------------

The inequality constraints in eq.~\eqref{eq:ilp-constraints} can be rewritten as an equality by introducing slack variables $s$ such that the ILP becomes
\begin{align}
 \vec x_0 = \mathrm{arg} & \min(\sum_i c_i x_i)\,,
\end{align}
subject to
\begin{align}                                                 & \sum_i A_{a i}x_i + s_a + b_a = 0, \\
  & s_a \in \mathbb{N},                \\
  & x_i \in \mathbb{N}.
\end{align}
While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{N}$ given fixed precision coefficients $A_{ij}$ and $b_i$.
As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values as allowed by Eq.~(\ref{eq:int_to_bin}).

@@

%----------------------------------------------------------------------------------------
\subsubsection{Integer Programming Mapping QUBO}
\label{sec:methods:ilp-qubo}
%----------------------------------------------------------------------------------------

The integer quadratic optimization problem can be mapped to a minimization of the quadratic objective function
\begin{align}
 \chi^2                         & = \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
 \nonumber                                                                                                                             \\ \label{eq:qubo-min}
                                & \qquad\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],   \\
 \vec x_0                       & =  T^x \vec \Psi^x_0 \, ,
 \\
 (\vec \Psi^x_0, \vec \Psi^s_0) & = \mathrm{arg}\min\limits_{\vec{\Psi}}(\chi^2) \,,                                                 &
\end{align}
where $p$ is an external parameter representing the strength of the penalty when violating constraints.
The objective function can be represented as a QUBO Hamiltonian
\begin{align}
 E =    &
 \begin{pmatrix}
  \Psi^x & \Psi^s
 \end{pmatrix}
 \begin{pmatrix}
  Q_{xx} & Q_{xs} \\
  Q_{sx} & Q_{ss}
 \end{pmatrix}
 \begin{pmatrix}
  \Psi^x \\ \Psi^s
 \end{pmatrix} + pb^2, \\
 \equiv & \Psi^T Q \Psi + C,
 \label{eq:matrix_form}
\end{align}
where
\begin{align}
 Q_{xx} = & {T^{x}}^T \left[ d + p A^T A + p \mathrm{Diag}_{x} \left(A^T b + b^T A\right) \right] T^x \nonumber \\
          & + \mathrm{Diag}_{\psi^x}(c) T^x,                                                                    \\
 Q_{xs} = & Q_{sx}^T = p {T^{x}}^T A^T T^s,                                                                     \\
 Q_{ss} = & p\left[ {T^{s}}^T T^s + \mathrm{Diag}_{\psi^s}\left( {T^{s}}^T b + b^T T^s\right) \right].
\end{align}
The function $\mathrm{Diag}_{z}(v)$ embeds a vector $v$ into a diagonal matrix in subspace $z$, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.

%----------------------------------------------------------------------------------------
\subsubsection{Comment on penalty term}
\label{sec:methods:ilp-qubo-comments}
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
\subsection{Example: Minimum Dominating Set Problem}
\label{sec:methods:mds}
%----------------------------------------------------------------------------------------

This section demonstrates the formalism in case of an example ILP: the Minimum Dominating Set problem.

%----------------------------------------------------------------------------------------
\subsubsection{Definition of the Minimum Dominating Set Problem}
\label{sec:methods:mds-def}
%----------------------------------------------------------------------------------------

Given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, and a subset of vertices $D \subseteq V$.
If the set of all vertices not in $D$ is adjacent to at least one vertex in $D$, then $D$ is a dominating set.
This is equivalent to requiring the set of nearest-neighbor vertices of $D$ (exclusive) and $D$ cover all vertices $N(D) \cup D = V$ (an example is given by Fig.~\ref{fig:dominating_sets}a).
The set $D$ is a minimal dominating set if there is no proper subset of $D$ that is a dominating set, {\it{i.e.}}, the removal of any vertex in $D$ results in $N(D) \cup D  \neq V$.
An example is given by Fig.~\ref{fig:dominating_sets}b.
The domination number of $D$ is given by the cardinality of $|D| \equiv \overline{\overline{D}}$.
The minimum dominating set (MDS) is defined by $D$ with the smallest domination number.
Fig.~\ref{fig:dominating_sets}c shows an example of the minimum dominating set of $G(V, E)$ and is different from the minimal dominating set.
We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the minimum dominating set, in general, can have a smaller domination number.
As a result, the solution to the dominating set problem can not be obtained by solving for the maximum independent set, a problem that is well studied for quantum annealers~\cite{}.

For general graphs, existing "classical" algorithms either find minimal solutions in exponential time $\sim O( 1.5^n)$ \cite{Fomin2009, vanRooij2009} or approximate solutions in polynomial time. For example, greedy algorithms locally optimize decisions about which nodes to add to the dominating set.
Thus one is guaranteed to find a dominating set but not necessarily a MDS. {\color{red} Write some pseudo code for greedy search.}
%We demonstrate an example greedy algorithm in figure Fig.~\ref{fig:mds-greedy}.

\iffalse
\begin{figure*}
 \centering
 \begin{tabular}{p{0.22\textwidth}p{0.22\textwidth}p{0.22\textwidth}p{0.22\textwidth}}
  \includegraphics[width=0.20\textwidth]{./figures/greedy-1.pdf}
                   &
  \includegraphics[width=0.20\textwidth]{./figures/greedy-2.pdf}
                   &
  \includegraphics[width=0.20\textwidth]{./figures/greedy-3.pdf}
                   &
  \includegraphics[width=0.20\textwidth]{./figures/greedy-4.pdf}            \\
  \centering\bf{a} & \centering\bf{b} & \centering\bf{c} & \centering\bf{d}
 \end{tabular}
 \caption{
  Example of greedy MDS algorithm:
  The algorithm iteratively adds vertices to the dominating set (black nodes) such that newly added nodes are maximally unconnected (white nodes).
  Connected nodes are neighbors of the DS (turquoise) or already in the DS.
  In (a), one finds three maximally unconnected nodes [(2), (4), (7)] which are adjacent to three unconnected nodes each.
  In the first step $a\to b$, randomly the node (4) is picked.
  In (b), one has three unconnected choices [(1), (2)] with each adjacent to another unconnected node and one node [(6)] which is only adjacent to neighbors of the DS.
  After randomly selecting (2) when going from $b \to c$, only one unconnected node is remaining (6).
  The found solution is a (minimal) dominating set but not a MDS.
  To find the MDS using this greedy algorithm, the first node choice must be either (2) or (5).
 }
 \label{fig:mds-greedy}
\end{figure*}
\fi

@@

@@

%----------------------------------------------------------------------------------------
\subsubsection{Modified annealing schedule}
\label{sec:methods:annealing-schedule}
%----------------------------------------------------------------------------------------

A quantum annealer evolves the ground state of an initial Hamiltonian into the ground state of the problem Hamiltonian by adiabatically changing the hardware which implements Hamiltonian.
Thus, the implemented Hamiltonian is explicitly time dependent
\begin{equation}
 H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
\end{equation}
and $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, while $H^\textrm{problem}$ is given by Eq.~(\ref{eq:matrix_form}) for the MDS application.
The variable $s\in [0, 1]$ is the normalized annealing time and, in physical units, is allowed to vary between 1$\mu s$ to 2$ms$ on DWave.

On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits ($B(s) \to B_i(s)$).
In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
The time dependent coefficients are nonlinear in time because the underlying control variable $c(s)$ which is designed to grow the persistent current $I_p(s)$ linearly in time.
The effective time delay is implemented by introducing an offset as $c(s) + \delta$.
As a result, systematic errors are introduced because the final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
Additionally, the values of the coefficients are unknown outside of $s\in [0, 1]$.
We extrapolate their values by a linear extrapolation, and only employ negative offsets such that this effect only enters at the beginning of the annealing process rather than the end.
Details of the DWave annealing schedule use to generate Fig.~\ref{fig:anneal_schedule} and further documentation are provided by DWave in Ref.~\cite{dwave_as, dwave_as_docu}.

The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system, in general, will exhibit more disorder.
When recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
\begin{equation}
 H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i,
\end{equation}
we recognize that if $h_i$ is randomly drawn from a Bernoulli distribution, we recover the spin-glass model.
The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization (MBL)~{\color{red} cite some AL papers here}.

%----------------------------------------------------------------------------------------
\subsubsection{Implementation of annealing offsets}
\label{sec:methods:annealing-schedule}
%----------------------------------------------------------------------------------------

For even the smallest graph $NN(2)$, the MDS problem is not native to the chimera graph and must be embedded. Following the hypothesis of MBL, we therefore, must look at the values of $h_i$ after embedding. The qubits then split into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| - \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific embedding. Further detail is given in Sec.~\ref{sec:methods:minor_embedding} {\color{red} put in methods more details}. We study the effects offset the two groups of qubits over a total range between 0\% and 5\% of $c$. The results of this study is shown in Fig.~\ref{fig:dwave_offset}.

The results in yellow (green) delays the annealing of qubits subject to stronger (weaker) external fields. We observe improvement (diminishment) in the experimental results when qubits subject to stronger (weaker) final external fields are delayed in the anneal schedule, in agreement with the MBL hypothesis. The phenomena is observed across different problem sizes and hints at the possibility of a generic improvement strategy. In the following section, we provide evidence that the improvement is rooted in quantum mechanics, and not other causes such as imperfections in hardware~\cite{} {\color{red} cite dwave's use of annealing offsets}. The master equation for quantum annealing is solved subject to the DWave anneal schedule with annealing offsets in order to reproduce the observed phenomenon.

@@

%----------------------------------------------------------------------------------------
\subsection{Finding the Dominating Set with a Quantum Annealer}
\label{sec:discussion:qa}
%----------------------------------------------------------------------------------------
\begin{figure}[b]
	\centering
	\begin{tabular}{cc}
	$G(n):$ &
	\raisebox{-.4\height}{\includegraphics[width=0.8\columnwidth]{./new_figures/linear_graph.pdf}}
	\end{tabular}
	\caption{Linear graphs $G(n)$ used in this study. Nodes denote vertices of the graphs and lines are undirected edges.}
\label{fig:linear}
\end{figure}

%----------------------------------------------------------------------------------------
\subsection{Decoherence and Many-Body Localization}
%----------------------------------------------------------------------------------------

>>>>

Integer linear programming (ILP) is an integer optimization problem subject to inequality constraints
\begin{align}
 \label{eq:initial-ip-def}
 \vec x_0 = \mathrm{arg} & \min\limits_{x}(\sum_i c_i x_i)
\end{align}
subject to
\begin{align}
 \label{eq:ilp-constraints}
  & \sum_i A_{ai}x_i +b_a \leq 0 \,, \\
  & x_i  \in \mathbbm{N}\, ,
\end{align}
where the natural numbers $\mathbbm{N}$ include zero, $i=1, \cdots,  N$ is the number of dependent variables and $a=1, \cdots, M$ the number of constraint equations.

ILP is a commonly tackled problem applicable to situations such as x~\cite{}, y~\cite{}, and the Minimum Dominating Set Problem (MDS)~\cite{}.
In general, however, ILP is classically NP-complete, and as a result, heuristic methods are employed~\cite{}.
Standard classical heuristic algorithms employ a greedy scheme which iteratively approximates optimal solutions--starting from a random initial guess, these algorithms apply locally optimal choices at each step.
The NP-hardness of ILP can be understood by realizing that while the solution to an $n$-dimensional linear problem can be obtained in polynomial time, the optimal integer solution in general must be found in the $2^n$ integer solutions which surround the real number solution.
While greedy algorithms do not guarantee optimal global solutions, they find approximate solutions in polynomial time, which can be utilized in further computations.

An important ILP is the Minimum Dominating Set problem which is represantivly considered in this work.
For a given a graph $G(E,V)$, defined by the set of $V$ vertices and $E$ edges, and a dominating set $D$ is a specific subset of vertices $D \subseteq V$.
In particluar $D$ is a dominating set if all vertices in $V$ but not in $D$ are adjacent to at least one vertex in $D$.
This is equivalent to requiring the set of nearest-neighbor vertices of $D$ (exclusive) and $D$ cover all vertices $N(D) \cup D = V$ (an example is given by Fig.~\ref{fig:dominating_sets}a).
The set $D$ is a minimal dominating set if there is no proper subset of $D$ that is a dominating set, {\it{i.e.}}, the removal of any vertex in $D$ results in $N(D) \cup D  \neq V$.
An example is given by Fig.~\ref{fig:dominating_sets}b.
The domination number of $D$ is given by the cardinality of $|D| \equiv \overline{\overline{D}}$.
The minimum dominating set (MDS) is defined by $D$ with the smallest domination number.
Fig.~\ref{fig:dominating_sets}c shows an example of the minimum dominating set of $G(V, E)$ and is different from the minimal dominating set.
We emphasize that while the maximum independent set is always a minimal dominating set as exemplified by Fig.~\ref{fig:dominating_sets}b, the minimum dominating set, in general, can have a smaller domination number.
As a result, the solution to the dominating set problem can not be obtained by solving for the maximum independent set, a problem that is well studied for quantum annealers~\cite{}.

For general graphs, existing "classical" algorithms either find MDS solutions in exponential time $\sim O( 1.5^n)$ \cite{Fomin2009, vanRooij2009} or approximate solutions in polynomial time. For example, greedy algorithms locally optimize decisions about which nodes to add to the dominating set.
Thus one is guaranteed to find a dominating set but not necessarily a MDS.

Due to the importance and difficulty, in this work, we present a method to obtain the optimal solution to ILP by employing methods of quantum annealing.

@@

In this paper, we propose a new algorithm that maps ILP problems to QUBOs.
This is achieved by the introduction of slack variables $s$ which turn the inequalities eq.~\eqref{eq:ilp-constraints} to equalities
\begin{align}
  & \sum_i A_{a i}x_i + s_a + b_a = 0, \\
  & s_a \in \mathbb{N},                \\
  & x_i \in \mathbb{N}.
\end{align}
As a result, we can restrict both $x_i$ and $s_i$ to sample over only positive integer values.

@@

A quantum annealer evolves the ground state of an initial Hamiltonian into the ground state of the problem Hamiltonian by adiabatically changing the hardware which implements Hamiltonian.
Thus, the implemented Hamiltonian is explicitly time dependent
\begin{equation}
 H(s) = A(s) H^{\textrm{init}} + B(s) H^{\textrm{problem}}, \label{eq:tdhamiltonian}
\end{equation}
and $H^\textrm{init}=\sum_i\sigma^x_i$ on the DWave, while $H^\textrm{problem}$ encodes the problem to be solved.
The variable $s\in [0, 1]$ is the normalized annealing time and, in physical units, is allowed to vary between 1$\mu s$ to 2$ms$ on DWave.

On DWave solvers, annealing offsets effectively advance or delay the annealing schedule of individual qubits ($B(s) \to B_i(s)$).
In Fig.~\ref{fig:anneal_schedule}, the default DWave annealing schedule is shown in black, in addition to the effects of applying negative offsets (effective time delay) to $A(s)$ and $B(s)$ in blue.
Details of the DWave annealing schedule use to generate Fig.~\ref{fig:anneal_schedule} and further documentation are provided by DWave in Ref.~\cite{dwave_as, dwave_as_docu}.

To improve annealing results we propose a qubitwise offsets associated with exeternal field alignments.
The motivation behind implementing per-qubit level offsets is rooted in the hypothesis that as the problem Hamiltonian is turned on, the system, in general, will exhibit more disorder.
When recasting the QUBO into its Ising form such that the problem Hamiltonian has the form
\begin{equation}
 H^{\textrm{Ising}} = \sum_{ij} J_{ij} \sigma^z_i \sigma^z_j + \sum_i h_i \sigma^z_i,
\end{equation}
we recognize that if $h_i$ is randomly drawn from a Bernoulli distribution, we recover the spin-glass model.
The spin-glass model enters its glassy state when $|h_i|$ is large, and as a consequence, the wavefunction experiences many-body localization effects, the many-body analogue of Anderson Localization (MBL)~{\color{red} cite some AL papers here}.

@@

 and present an example implementation in case of the Minimal Dominating Set problem (\ref{sec:methods:mds}).
We review the annealing process on the utilized hardware (\ref{sec:methods:annealing}) and describe the computational framework which we used to simulate the annealing process (\ref{sec:methods:simulation}).
Section \ref{sec:results} summarizes our findings and presents...
We conclude this report in \ref{sec:conclusion}.
All algorithms used and data obtained are publicly available (\ref{sec:open-source})

%----------------------------------------------------------------------------------------
\subsection{ILP QUBO}
\label{sec:results:qa}
%----------------------------------------------------------------------------------------

The integer quadratic optimization problem can be mapped to a minimization of the quadratic objective function
\begin{align}
 \chi^2                         & = \left[\Psi^x_{\mu} T^x_{\mu i}d_{ij} T^x_{j \nu}\Psi^x_\nu + c_i T^x_{i\mu} \Psi^x_\mu \right.
 \nonumber                                                                                                                             \\ \label{eq:qubo-min}
                                & \qquad\left.+ p (A_{a b} T^x_{b \mu} \Psi^x_{\mu} + T^s_{a \alpha} \Psi^s_\alpha + b_a)^2 \right],   \\
 \vec x_0                       & =  T^x \vec \Psi^x_0 \, ,
 \\
 (\vec \Psi^x_0, \vec \Psi^s_0) & = \mathrm{arg}\min\limits_{\vec{\Psi}}(\chi^2) \,,                                                 &
\end{align}
where $p$ is an external parameter representing the strength of the penalty when violating constraints and $T^{x,z}$ is a matrix mapping qubits to integers (see also section \ref{sec:methods:bit-basis}).
The objective function can be represented as a QUBO Hamiltonian
\begin{align}
 E =    &
 \begin{pmatrix}
  \Psi^x & \Psi^s
 \end{pmatrix}
 \begin{pmatrix}
  Q_{xx} & Q_{xs} \\
  Q_{sx} & Q_{ss}
 \end{pmatrix}
 \begin{pmatrix}
  \Psi^x \\ \Psi^s
 \end{pmatrix} + pb^2, \\
 \equiv & \Psi^T Q \Psi + C,
 \label{eq:matrix_form}
\end{align}
where
\begin{align}
 Q_{xx} = & {T^{x}}^T \left[ d + p A^T A + p \mathrm{Diag}_{x} \left(A^T b + b^T A\right) \right] T^x \nonumber \\
          & + \mathrm{Diag}_{\psi^x}(c) T^x,                                                                    \\
 Q_{xs} = & Q_{sx}^T = p {T^{x}}^T A^T T^s,                                                                     \\
 Q_{ss} = & p\left[ {T^{s}}^T T^s + \mathrm{Diag}_{\psi^s}\left( {T^{s}}^T b + b^T T^s\right) \right].
\end{align}
The function $\mathrm{Diag}_{z}(v)$ embeds a vector $v$ into a diagonal matrix in subspace $z$, and absorbs the linear contributions of the QUBO into the diagonal elements of the quadratic representation.

A solution to the ILP is found by obtaining the qubit vector $\psi$ which minimizes $E$.
The integer solution to the original ILP is computed by $\vec x = T^x \vec \psi^x$ and the original energy is computed by shifting the annealer extracted energy by $pb^2$.
The slack components of this vector $\psi^s$ can be utilized to check if the contraints are indeed fulfilled.

%----------------------------------------------------------------------------------------
\subsection{Dominating Set scaling \& offset study}
\label{sec:results:qa}
%----------------------------------------------------------------------------------------
\begin{figure}[b]
	\centering
	\begin{tabular}{cc}
	$G(n):$ &
	\raisebox{-.4\height}{\includegraphics[width=0.8\columnwidth]{./new_figures/linear_graph.pdf}}
	\end{tabular}
	\caption{Linear graphs $G(n)$ used in this study. Nodes denote vertices of the graphs and lines are undirected edges.}
\label{fig:linear}
\end{figure}

For even the smallest graph $G(2)$, the MDS problem is not native to the chimera graph and must be embedded. Following the hypothesis of MBL, we therefore, must look at the values of $h_i$ after embedding. The qubits then split into two groups depending on the value of $h_i$ relative to $(\textrm{max}|\{h\}| + \textrm{min}|\{h\}|) / 2$ given the set of external magnetic fields $\{h\}$ defined by a specific embedding. Further detail is given in Sec.~\ref{sec:methods:minor_embedding} {\color{red} put in methods more details}. We study the effects offset the two groups of qubits over a total range between 0\% and 5\% of $c$. The results of this study is shown in Fig.~\ref{fig:dwave_offset}.

The results in yellow (green) delays the annealing of qubits subject to stronger (weaker) external fields. We observe improvement (diminishment) in the experimental results when qubits subject to stronger (weaker) final external fields are delayed in the anneal schedule, in agreement with the MBL hypothesis. The phenomena is observed across different problem sizes and hints at the possibility of a generic improvement strategy.

%----------------------------------------------------------------------------------------
\subsubsection{Comment on ILP QUBO penalty term}
\label{sec:methods:ilp-qubo-comments}
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
\subsection{Integer Programming Mapping to QUBO}
\label{sec:methods:ilp}

@@

@@

%----------------------------------------------------------------------------------------
\subsection{Notes}
\label{sec:methods:ilp:notes}
%----------------------------------------------------------------------------------------

While the coefficients of the inequality constraints are not required to be integer valued, the inequalities can be trivially rescaled such that $s_i \in \mathbbm{N}$ given fixed precision coefficients $A_{ij}$ and $b_i$.

@@

%----------------------------------------------------------------------------------------
\subsubsection{Finite Annealing Schedules}
\label{sec:methods:annealing-schedule}
%----------------------------------------------------------------------------------------
The time dependent coefficients are nonlinear in time because the underlying control variable $c(s)$ which is designed to grow the persistent current $I_p(s)$ linearly in time.
The effective time delay is implemented by introducing an offset as $c(s) + \delta$.
As a result, systematic errors are introduced because the final values of $A(s)$ and $B(s)$ will differ for qubits with different offsets.
Additionally, the values of the coefficients are unknown outside of $s\in [0, 1]$.
We extrapolate their values by a linear extrapolation, and only employ negative offsets such that this effect only enters at the beginning of the annealing process rather than the end.

@@
